Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-16 surfaces-write-up/surface-write-up.tex

\begin{rem}
\label{rem:proj-one-point-ind}
Note that the method of proof for Theorem ~\ref{thm:proj-one-point}
can be immediately generalized to work inductively. If $D = D' + H$
for some hyperplane $H$, then we can use the proof above to show
the canonical ring $R_D$ is generated over $R_D'$ by the same
generators and with the same relations given in Theorem
~\ref{thm:proj-one-points}.
\end{rem}

\begin{thm}
\label{thm:proj-effective}
Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i H_i$, with $\alpha_i =
\frac{p_i}{q_i} \in \bq$ and each $H_i$ a hypersurface of
$\bp^m$, be an effective divisor on $\bp^m$.

>>>>

\begin{rem}
\label{rem:proj-one-point-ind}
Note that the method of proof for Theorem ~\ref{thm:proj-one-point}
can be immediately generalized to work inductively. If $D = D' + H$
for some hyperplane $H$, then we can use the proof above to show
the canonical ring $R_D$ is generated over $R_D'$ by the same
generators and with the same relations given in Theorem
~\ref{thm:proj-one-point}.
\end{rem}

\begin{thm}
\label{thm:proj-effective}
Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i C_i$, with $\alpha_i =
\frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
$\bp^m$, be an effective divisor on $\bp^m$.
